---
title: "data607_assignment3"
author: "karmaGyatso"
date: '2022-09-17'
output: html_document
---
```{r}
library(tidyverse)
```

## #1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"
```{r}
csv_data <- read.csv('https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/grad-students.csv')

glimpse(csv_data)
```
```{r}
string_match <- csv_data %>% 
  filter(str_detect(Major, "DATA|STATISTIC")) %>%
  head()
  
string_match
```

## #2 Write code that transforms the data below:
[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry" 
[13] "olive"        "salal berry"

**Into a format like this:**

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r}
str_fruits <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"'
str_fruits_pattern <- str_extract_all(str_fruits,pattern = '[A-Za-z]+.?[A-Za-z]+')
str_fruits_pattern <- unlist(str_fruits_pattern)

str_fruits_pattern 
```

```{r}
newformat <- str_c(str_fruits_pattern, sep = ",", collapse = "\", \"")
newformat <-  paste("c(\"", newformat,"\")")
newformat <- str_replace(newformat, " b", "b")
newformat <- str_replace(newformat, "y ", "y")
cat(newformat)
```

## #3 Describe, in words, what these expressions will match:

```{r}
test_string <- c('aaa', 'bbb', 'cat', 'doll', 'aba', 'cda', 'kind', 'noon', 'moon','byby', 'axaxa','racecar')
```

### (.)\1\1
**It will display any character that is repeated 3 times  **

```{r}
str_match(test_string, '(.)\\1\\1')
```



### (.)(.)\\2\\1

**same letter before and after of 2 same character**
```{r}
str_match(test_string, '(.)(.)\\2\\1')
```

### (..)\1
**Regular expression not represented in string format that has two characters repeated twice in the same order**
```{r}
str_match(test_string, '(..)\\1')
```

### "(.).\\1.\\1"
**The letter is located that has any letter after it. Then the letter with any letter with the repeated letter**
```{r}
str_match(test_string, '(.).\\1.\\1')
```

### "(.)(.)(.).*\\3\\2\\1"
**letters follows by same three letters but the third swap the position with the first letter**
```{r}
str_match(test_string, '(.)(.)(.).*\\3\\2\\1')

```

## #4 Construct regular expressions to match words that:

```{r}
pr4_str <- c('wow', 'ada', 'peep', 'mama', 'kaka', 'eleven', 'rarer')
```

### Start and end with the same character. 

```{r}
str_match(pr4_str, "^(.).*\\1$")
```

### Contain a repeated pair of letters (e.g. “church” contains “ch” repeated twice.) 

```{r}
str_match(pr4_str, "(..).*\\1")
```

### Contain one letter repeated in at least three places (e.g. “eleven” contains three “e”s.) 

```{r}
str_match(pr4_str, "(.).*\\1.*\\1")

```

