---
title: "Data607_assignment2"
author: "karmaGyatso"
date: '2022-09-09'
output:
  pdf_document: default
  html_document: default
---


```{r}
library(RMySQL)
library(dplyr)
```
## Requirement

Installation of MySQL is required to run MySQL, which are provided in my GitHUB. Link is provided: 

https://github.com/karmaggyatso/CUNY_SPS/tree/main/Github_data607/ASSIGNMENT2

# Additional Information

While running the SQL script, please change the dbname, host, port, user and password as per configuration

Password is protected in this project. You can simply use you db password to access the files. 

## Introduction

I gathered a list of six recent movie names and asked 5 friends and neigbor if they have watched any of them and rate it. 

In the MYSQL database, I created 4 tables which are GENRE, MOVIES, PERSON AND REVIEWS. 

In the code below, I have established a connection to MySQL database and it requires to enter a password because I didn't wanted to reveal it. 

```{r}
mysqlconnection = dbConnect(RMySQL::MySQL(),
                            dbname='movies',
                            host='127.0.0.1',
                            port=3306,
                            user='root',
                            password=rstudioapi::askForPassword("database password"))

```

## MOVIES TABLE
In the MOVIES table, there are list of 6 movie titles with their genre. The FOREIGN KEY is GENRE_ID in the MOVIES table.

## GENRE TABLE
Genre consist of 7 types and ID column in it, which is FOREIGN KEY  in MOVIES table

## PERSON TABLE
Person table consist of name of people who volunteered to rate the movies. ID is FOREIGN KEY in Reviews table.

## REVIEWS TABLE
In the table, we have column id, name_id FOREIGN KEY REFERENCES PERSON(ID), movie_id FOREIGN KEY REFERENCES MOVIES(ID), and review
```{r}
dbListTables(mysqlconnection) 
```

## Getting data from the Database
I used join condition to join all the tables and get one complete data set and fetch it and store in the data.frame
```{r}
result <- dbSendQuery(mysqlconnection, "SELECT M.MOVIE_TITLE AS MOVIE_TITLE, A.GENRE_TITLE AS GENRE, C.NAME AS NAME, B.REVIEW AS RATING FROM MOVIES M
JOIN GENRE A ON A.ID = M.GENRE_ID
JOIN REVIEWS B ON B.MOVIE_ID = M.ID 
JOIN PERSON C ON C.ID = B.NAME_ID;")
```


```{r}
data<-fetch(result)
print(data)
```

## Most loved
Among the six movies, most of them loved PINOCCHIO, which falls under drama GENRE. The rating is 3.75. The dataset is arranged in DESC order. 
```{r}
data %>%
    filter(!is.na(RATING) ) %>%
      group_by(MOVIE_TITLE) %>% 
        summarise(avg_rating = mean(RATING)) %>%
          arrange(desc(avg_rating))
```
## Most Watched
Even though PINOCCHIO is most loved, it competes with THOR: LOVE AND THUNDER in most watched catagory. 
```{r}
data %>%
    filter(!is.na(RATING) ) %>%
      group_by(MOVIE_TITLE) %>% 
        count(MOVIE_TITLE, sort=TRUE)
```
## Most watched GENRE
The most watched GENRE is action. Followed by Adventure. 
```{r}
most_watched_genre <- data %>%
    filter(!is.na(RATING) ) %>%
      group_by(GENRE) %>% 
        count(GENRE, sort=TRUE)
most_watched_genre
```



