---
title: "Week11_Assignment"
author: "karmaGyatso"
date: '2023-04-16'
output: html_document
---

```{r}
path = "https://raw.githubusercontent.com/karmaggyatso/CUNY_SPS/main/data_605/week_12/who.csv"
csv_data = read.csv(path)

head(csv_data)
```

```
1. Provide a scatterplot of LifeExp~TotExp, and run simple linear regression. Do not transform the
variables. Provide and interpret the F statistics, R^2, standard error,and p-values only. Discuss
whether the assumptions of simple linear regression met.
```
```{r}
model = lm(LifeExp ~ TotExp, data = csv_data)
plot(LifeExp ~ TotExp, data = csv_data, ylab = "Life Expectancy", xlab = "Total Expectancy") + 
  abline(model)
```

```{r}
summary(model)
```

F-statistic: 65.26 on 1 p-value: 7.714e-14 Multiple R-squared: 0.2577

The F-statistic is testing the model against the null model, and the p-value is the chance that, given the hypothesis is true, the data turned out the way it did. There is a very low chance of that, according to our p-value of 7.714e-14. The R-squared value indicates that about 25.77% of the variation in the response variable can be attributed to the independent variable.

```
2. Raise life expectancy to the 4.6 power (i.e., LifeExp^4.6). Raise total expenditures to the 0.06
power (nearly a log transform, TotExp^.06). Plot LifeExp^4.6 as a function of TotExp^.06, and r
re-run the simple regression model using the transformed variables. Provide and interpret the F
statistics, R^2, standard error, and p-values. Which model is "better?"
```

```{r}
mod_2 <- lm(I(LifeExp^4.6) ~ I(TotExp^0.06), data = csv_data)
summary(mod_2)
```

```{r}
plot(I(LifeExp^4.6) ~ I(TotExp^0.06), data = csv_data, ylab = "Life Expectancy", xlab = "Total Expectancy")+
abline(mod_2)
```
This adjustment increased our $R^2$ value to 72.83% and out F statistic to over 500, so it is already a better model than the first problem.

```
3. Using the results from 3, forecast life expectancy when TotExp^.06 =1.5. Then forecast life
expectancy when TotExp^.06=2.5.
```
```{r}
ForLifeExpt <- function (x){
  y <- mod_2$coefficients[1] + mod_2$coefficients[2] * x
  y <- y^(1/4.6)
  print(y)
}
ForLifeExpt(1.5)

```
```{r}
ForLifeExpt(2.5)
```

```
4. Build the following multiple regression model and interpret the F Statistics, R^2, standard error, and p-values. How good is the model?

  LifeExp = b0+b1 x PropMd + b2 x TotExp +b3 x PropMD x TotExp
```

```{r}
lm_fit <- lm(LifeExp ~ PropMD + TotExp + PropMD*TotExp, data = csv_data)
summary(lm_fit)
```

Since the p-value is smaller than .05, the model is statistically significant. The R2 value indicates that the independent variable accounts for 35.74% of the variability in the independent variable. The F value indicates that the model is strong

```
5. Forecast LifeExp when PropMD=.03 and TotExp = 14. Does this forecast seem realistic? Why or why not?
```

```{r}
(le <- (lm_fit$coefficients[1]) +  (lm_fit$coefficients[2]*0.03) + (lm_fit$coefficients[3]*14) - (lm_fit$coefficients[4]*0.03*14))

```

This forecast is unrealistic, considering the age of the person is 107 years old.
