---
title: "data607_assignment7"
author: "karmaGyatso"
date: '2022-10-29'
output: html_document
---

```{r}
library(httr)
library(jsonlite)
library(DT)
```

In this assignment, we are require to use the **New York Times** API and read the JSON data and transform in R dataframe. I have used NYT books API and generated the API KEY upon signing in the website. 

The process to use the API is provided [here] (https://developer.nytimes.com/docs/books-product/1/overview)

Below code shows the format to call the API. The URL is concatinated with api-key. 
```{r}
url <- 'https://api.nytimes.com/svc/books/v3/lists/current/hardcover-fiction.json'
api_key <- 'TBbi8eCy7Amyr926FiHGJZlEXYcgVUWr'

main_url <- paste(url,'?api-key=',api_key, sep = '')

```

Reading the JSON content from the URL. Flatten function remove the level of hierrachy from a list. The new variable class type is LIST. We need to convert to **data.frame**
```{r}
books_raw_list <- fromJSON(main_url, flatten = TRUE)
class(books_raw_list)
```



Creating the data frame from the JSON format list.
```{r}
books_df <- data.frame(books_raw_list$results$books)

class(books_df)
```

Selecting only couple of column header. 
```{r}
books_df_subset <- books_df[, c("rank", "title", "author", "price", "publisher", "primary_isbn13")]

books_df_subset
```
DT::datatable allows us to search and limit display result. 
```{r}
DT::datatable(books_df_subset)
```

